Efficient Handling of String-Number Conversion

### 2019-11-22 draft.tex
sec 6
sec 5

\changed{
We say that a mapping $e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $e = \parikhof{x}\cup I$
for some $x \in L(A)$ and $I\in\semof\paf$ such that $w = I(x)$.   
%
Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
%
We use $\encode \pa(w)$ below to denote all $\pa$-encoding of a word $w$,
and $\decode \pa (e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x}\}$$
	$$\decode \pa(e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, e = I \cup \parikhof{x} \}$$
Informally, that a word encoding $e$ belongs to $\encode \pa( w )$ means that $w$ is an interpretation of a parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $e$. 
Since $e$ only records the numbers of occurrences of character variables (Parikh image), 
the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(e)$.

If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
$$
w = \decode \pa (\encode \pa (w))
$$
Consequently, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.
%words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
}

@@

The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
\changed{
It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. The $\decode \dr$ function maps a word encoding $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint. Formally, $\dr (I_e\cup I_z) = I_s \cup I_z$, where $x\in X$,
$I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.

@@

\paragraph{Synchronization of PAs}
We will now discuss a construction of the \emph{synchronization formula} for two PAs $\pa$ and $\pa'$. 
It is a linear formula $\syncfof \pa {\pa'}$ 
that specifies how each word in the semantic intersection $\semof \pa \cap \semof {\pa'}$ is encoded by $\pa$ and by $\pa'$.
%
More precisely, the models of $\syncfof \pa {\pa'}$ represent pairs of word
encodings 
$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode \pa(w)$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).

>>>>

\changed{
We say that a mapping $I_e:\cvar\cup\#\cvar \rightarrow \nat$ is a \emph{word encoding} a word $w$ (or a $\pa$-encoding of $w$) if $w$ is an instantiation of some parametric word $x \in L(\pa)$ whose Parikh image and interpretation of character variables are defined by $I_e$.  
%
Conversely, $w$ is a \emph{$\pa$-decoding} of $e$.
%
We use $\encode \pa(w)$ below to denote all $\pa$-encodings of a word $w$,
and $\decode \pa (I_e)$ to denote all $\pa$-decodings of a word encoding $e$. Namely,  
% to \emph{word encodings} $e:\cvar\cup\#\cvar \rightarrow \nat$ via the PA $\pa$ and the function $\decode \pa$ does it in the reverse direction.
	$$\encode \pa( w ) = \{e \mid  x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x}\}$$
	$$\decode \pa(I_e) =\{ w \mid x \in L(\pa) , I(x) =w, I\in\semof \paf, I_e = I \cup \parikhof{x} \}$$

Since a word encoding $I_e$ only records the numbers of occurrences of character variables (Parikh image), 
the same word encoding may be shared by multiple words, as formalized in the definition of $\decode \pa(I_e)$.

If $\pa$ is a PFA, then by Lemma~\ref{lemma:decoding}, each word encoding $e\in \encode \pa( w )$ can be decoded uniquely to the word $w$, i.e.
$$
\{w\} = \decode \pa (\encode \pa (w))
$$
Consequently, as stated by the following corollary of Lemma~\ref{lemma:decoding}, 
Parikh image of parametric words in $L(A)$ paired with character variable interpretations satisfying $\paf$ encode precisely the words in $\semof{\pa}$.
%words in $\semof{\pa}$ are precisely the decodings of the Parikh image of parametric words in $L(A)$ paired with character variables interpretations satisfying $\paf$:
}

@@

The correctness of the entire construction of $\underf \dr {\insc}$ is expressed by  Theorem~\ref{theorem:correct}. 
\changed{
It uses the decoding function $\decode \dr$ parameterized by the domain restriction $\dr$. The $\decode \dr$ function maps a word encoding $I_e: V_\dr\cup\#V_\dr\rightarrow \nat$ paired with an interpretation of integer variables $I_z$ to a model $I_s \cup I_z$ of a string constraint. Formally, $\decode  \dr (I_e\cup I_z) = I_s \cup I_z$, where $x\in X$,
$I_s(x) = \decode {\dr(x)} ((I_e)_{V_{\dr(x)}\cup \#V_{\dr(x)}})$.

@@

\paragraph{Synchronization of PAs}
We will now discuss a construction of the \emph{synchronization formula} for two PAs $\pa$ and $\pa'$. 
It is a linear formula $\syncfof \pa {\pa'}$ 
that specifies how each word in the semantic intersection $\semof \pa \cap \semof {\pa'}$ is encoded by $\pa$ and by $\pa'$.
%
More precisely, the models of $\syncfof \pa {\pa'}$ represent pairs of word
encodings 
$e$ and $e'$ such that $e\in\encode \pa(w)$ and $e'\in\encode {\pa'} (w)$ (hence $w\in\semof{\pa}\cap\semof{\pa'}$).
